Unsupervised embeddings capture latent structure of scientific mobility

### 2020-02-24 paper/current/main.tex
add_contents_to_viualziation_para

%
% Figure - UMAP Projections
%
\begin{figure}[hp!]
	\centering
	\label{fig:projection}
	\includegraphics[width=\textwidth]{\figdir/Projection/big_embedding_picture.png}
	\caption{
		\textbf{Projection of embedding demonstrates complex multi-scale structure.}
		\textbf{a.}
		UMAP projection \cite{mcinnes2018umap} of the entire embedding space reveals geographic clustering.
		Each point corresponds to an organization. 
		Size indicates the size of the organization.
		Color indicates the continent. 
		We re-project subsets of organizational vectors to uncover more complex local structure.
		\textbf{b.} Re-projection of organizational vectors roughly corresponding to West-Asian, Southeast Asian, and South Asian countries. 
		\textbf{c.} Re-projection of organizations in Spain, Portugal, and the Portuguese- and Spanish-speaking countries South and Central America. 
		\textbf{d.} Re-projection of organizations in the United States reveal geographic clustering based on state.
		Color indicates Census Bureau-designated regions,
		\textbf{e.} Re-projection of organizations in Massachusetts reveal clustering based on organizational sector, prestige. 
		Color indicates sector designation of organization. 
	}
\end{figure}

@@

% $p(j|i)$ and ${\mu_j}$ is given from data, and the our model trains $\exp(\cos(v_i,v_j))$ with the data. Then, can we infer the functional form of the $p(j|i)$ which is written with the results of the model?

% Cosine similarity capture the relative importance of neighborhood, because, with same $p(j|i)$, if $\mu_j$ is large, $\exp(\cos(v_i,v_j)$ should small and if $\mu_j$ is small, $\exp(\cos(v_i,v_j)$ should be large. Based on this relationship, cosine similarity capture the relative importance. Simply, we can use $p(j|i)$ as just normalized importance with

% Also, we can validate this proxy with checking inverse relationship, \ref{eq:inverse_relationship}.

% \begin{equation}
%     \frac{f_{ij}}{\mu_i * \mu_j} \propto \frac{\exp(\cos(v_i, v_j))}{\mu_i * \sum_{w\in\mathpzc{N}_j} \exp(\cos(v_w,v_j))} \propto \exp(\cos(v_i,v_j))
% \end{equation}
% \begin{equation}
% \label{eq:inverse_relationship}
%      \mu_i * \sum_{w\in\mathpzc{N}_j} \exp(\cos(v_w,v_j)) \propto C
% \end{equation}

% According to Fig. \ref{fig:inverse_relationship}, $\mu_{i}$ and $\sum_{w \in \mathcal{N}_{j}} \exp(\cos(v_w \cdot v_j))$ have either a negative power-law relationship, or a weak inverse relationship. 
% This relationship may result form hub nodes, or major organizations central to the global network of co-affiliations. 
% A node with large $\mu_{i}$ would be considered a hub node in the network, and following the friendship paradox, neighboring nodes will likely have fewer neighbors than the hub.

% \begin{figure}
%     \centering
%     \includegraphics[width=0.8\columnwidth]{test.png}
%     \caption{Relationship between the conditional probability and the cosine similarity}
%     \label{fig:inverse_relationship}
% \end{figure}

>>>>

We visualize whole organization vectors in  Fig. \ref{fig:projection}a.
The coordinates of each organization come from a 2-D projection of the  embedding vectors with UMAP \cite{mcinnes2018umap} and the colors indicates the continent that organization belongs. Overall structure is almost similar to geographical map seen from the north pole while coherent structures of the communities are detected. For instance, french-spoken region of the Canada (Quebec, Montreal) is more close to French cluster rather than mainland of Canada.
%
% Figure - UMAP Projections
%
\begin{figure}[hp!]
	\centering
	\label{fig:projection}
	\includegraphics[width=\textwidth]{\figdir/Projection/big_embedding_picture.png}
	\caption{
		\textbf{Projection of embedding demonstrates complex multi-scale structure.}
		\textbf{a.}
		UMAP projection \cite{mcinnes2018umap} of the entire embedding space reveals geographic clustering.
		Each point corresponds to an organization. 
		Size indicates the size of the organization.
		Color indicates the continent. 
		We re-project subsets of organizational vectors to uncover more complex local structure.
		\textbf{b.} Re-projection of organizational vectors roughly corresponding to West-Asian, Southeast Asian, and South Asian countries. 
		\textbf{c.} Re-projection of organizations in Spain, Portugal, and the Portuguese- and Spanish-speaking countries South and Central America. 
		\textbf{d.} Re-projection of organizations in the United States reveal geographic clustering based on state.
		Color indicates Census Bureau-designated regions,
		\textbf{e.} Re-projection of organizations in Massachusetts reveal clustering based on organizational sector, prestige. 
		Color indicates sector designation of organization. 
	}
\end{figure}

@@
